Code used to generate paper results : Database comparison and CT characteristics

### 2024-06-21 Paper_code-Database_Comparison.Rmd
Small verif in CTdatabase analysis
Updated with new tumors thresholds

### Burggeman's list

@@

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/CTdatabase_comparison.pdf"))
plot(CTdatabase_ours, gp = gp)
upset(upset_CTdatabase,
      text.scale = upset_text_size)
dev.off()
```

@@

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Jamin_comparison.pdf"))
plot(core_ours, gp = gp)
upset(upset_Jamin,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Wang_comparison.pdf"))
plot(Wang_ours, gp = gp)
upset(upset_Wang,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Carter_comparison.pdf"))
plot(Carter_ours, gp = gp)
upset(upset_Carter,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Bruggeman_comparison.pdf"))
plot(Bruggeman_ours, gp = gp)
upset(upset_Bruggeman,
      text.scale = upset_text_size)
dev.off()
```

>>>>

### Bruggeman's list

@@

CTdatabase_lost$external_gene_name[!CTdatabase_lost$external_gene_name %in% unlist(CTdatabase_lost_upset)]

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/CTdatabase_comparison.pdf"))
plot(CTdatabase_ours, gp = gp)
upset(upset_CTdatabase,
      text.scale = upset_text_size)
dev.off()
```

@@

There is one gene (SPANXN1) that is missing (in 165 from CTdatabase lost) but 
that is not on the upset plot (164 on upset plot) as it was removed because of 
the TSS.

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Jamin_comparison.pdf"))
plot(core_ours, gp = gp)
upset(upset_Jamin,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Wang_comparison.pdf"))
plot(Wang_ours, gp = gp)
upset(upset_Wang,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Carter_comparison.pdf"))
plot(Carter_ours, gp = gp)
upset(upset_Carter,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Bruggeman_comparison.pdf"))
plot(Bruggeman_ours, gp = gp)
upset(upset_Bruggeman,
      text.scale = upset_text_size)
dev.off()
```
